---
title: "R-based Workshop Specifications"
format: html
date-modified: last-modified
---


This page outlines the software requirements and specifications for R-based workshops.


## Fully R/RStudio based workshops:

- [Introduction to R for Bioinformatics](https://github.com/GenomicsAotearoa/Introduction-to-R)  
- [Intermediate R for Bioinformatics](https://github.com/GenomicsAotearoa/Intermediate-R)   
- [Visualisation with ggplot2](https://github.com/GenomicsAotearoa/visualization_day)   

**All packages needed across these workshops:**


```{r}
#| eval: false

install.packages("tidyverse")
install.packages("palmerpenguins")
install.packages("viridis")
install.packages("devtools")
devtools::install_github("G-Thomson/Manu")
install.packages("scales")
install.packages("ggbeeswarm")
install.packages("ggridges")
install.packages("vegan")

```

**Load libraries:**

```{r}
#| eval: false

library(tidyverse)
library(palmerpenguins)
library(viridis)
library(devtools)
library(Manu)
library(scales)
library(ggbeeswarm)
library(ggridges)
library(vegan)
```



## Individual workshop set-up 

### Introduction to R

GitHub {{< fa brands github >}}: [https://github.com/GenomicsAotearoa/Introduction-to-R](https://github.com/GenomicsAotearoa/Introduction-to-R)

**General description:** This workshop uses primarily base R tools and default packages installed in RStudio. It uses one example dataset, which needs to be pre-loaded on the REANNZ training environment in `R4Genomics` dir, but there is also a [direct github link included in the material](https://genomicsaotearoa.github.io/Introduction-to-R/03-basics-dataframes-manipulation/#importing-tabular-data-into-r). Only one additional library is needed, which is `ggplot2.` 

#### **Packages/libraries**

```{r}
#| eval: false

install.packages("ggplot2")

```


```{r}
#| eval: false

library(ggplot2)
```

#### Dataset

- The `combined_tidy_vcf.csv` is available on GitHub here: [https://github.com/GenomicsAotearoa/Introduction-to-R/blob/main/combined_tidy_vcf.csv](https://github.com/GenomicsAotearoa/Introduction-to-R/blob/main/combined_tidy_vcf.csv)

Load in R: 

```{r}
#| eval: false

variants <- read.csv("https://raw.githubusercontent.com/GenomicsAotearoa/Introduction-to-R/refs/heads/main/combined_tidy_vcf.csv")
```

\ 

### Visualisation with ggplot2

GitHub {{< fa brands github >}}: [https://github.com/GenomicsAotearoa/visualization_day](https://github.com/GenomicsAotearoa/visualization_day)

**General description:** This workshop uses tidyverse tools and some extra packages for colours and geoms. It uses one example dataset, which is not pre-loaded on the REANNZ training environment and is supplied [in the material as a direct github link](https://genomicsaotearoa.github.io/visualization_day/viz_4_building_better.html#the-data). Many tidyverse tools are needed in this workshop (`ggplot2`, `dplyr`, `lubridate`, `forcats` etc) so we recommend installing all tidyverse. 


#### **Packages/libraries**

```{r}
#| eval: false

install.packages("tidyverse")
install.packages("palmerpenguins")
install.packages("viridis")
install.packages("devtools")
devtools::install_github("G-Thomson/Manu")
install.packages("scales")
install.packages("ggbeeswarm")
install.packages("ggridges")
```


```{r}
#| eval: false

library(tidyverse)
library(palmerpenguins)
library(viridis)
library(Manu)
library(scales)
library(ggbeeswarm)
library(ggridges)
library(glue)


```


#### Dataset

- The `eDNA_group_counts.tsv` file is available on GitHub here: [https://github.com/GenomicsAotearoa/visualization_day/blob/main/data/eDNA_group_counts.csv](https://github.com/GenomicsAotearoa/visualization_day/blob/main/data/eDNA_group_counts.csv)

Load in R: 

```{r}
#| eval: false
top_group_counts <- read.delim("https://raw.githubusercontent.com/GenomicsAotearoa/visualization_day/refs/heads/main/data/eDNA_group_counts.tsv")
```

\


### Intermediate R for bioinformatics

GitHub {{< fa brands github >}}: [https://github.com/GenomicsAotearoa/Intermediate-R](https://github.com/GenomicsAotearoa/Intermediate-R)

**General description:** This workshop uses multiple `tidyverse` tools and `vegan`, in addition to base R/default RStudio packages. It uses three example datasets, which are not pre-loaded on the REANNZ training environment and are supplied [in the material as direct github links](https://genomicsaotearoa.github.io/Intermediate-R/0.prep/). 

#### **Packages/libraries**

```{r}
#| eval: false

install.packages("tidyverse")
install.packages("vegan")

```


```{r}
#| eval: false

library(tidyverse)
library(vegan)
```

#### Dataset

- The three datasets `asv_table.tsv`, `env_table.tsv`and `taxonomy.tsv` are available on GitHub here: [https://github.com/GenomicsAotearoa/Intermediate-R/tree/main/tables](https://github.com/GenomicsAotearoa/Intermediate-R/tree/main/tables)

Load in R: 

```{r}
#| eval: false

asv <- read.delim("https://raw.githubusercontent.com/GenomicsAotearoa/Intermediate-R/main/tables/asv_table.tsv")
env <- read.delim("https://raw.githubusercontent.com/GenomicsAotearoa/Intermediate-R/main/tables/env_table.tsv")
tax <- read.delim("https://raw.githubusercontent.com/GenomicsAotearoa/Intermediate-R/main/tables/taxonomy.tsv")
```

\ 

# **WORK IN PROGRESS...**

### Partially R/RStudio based workshops
- [RNA-seq (yeast dataset)](https://github.com/GenomicsAotearoa/RNA-seq-data-analysis-workflow)
- [RNA-seq (NZ dataset)](https://github.com/GenomicsAotearoa/RNA-seq-data-analysis-workflow-NZ)
- [Reproducibility with Git and Quarto](https://github.com/GenomicsAotearoa/reproducibility_with_git_and_quarto)


```{r}
#| eval: false

install.packages("tidyverse")
install.packages("BiocManager")

BiocManager::install("limma")
BiocManager::install("edgeR")
BiocManager::install("DESeq2")
BiocManager::install("gplots")
BiocManager::install("goseq")
install.packages("ggiraph")
install.packages("plotly")

```

```{r}
#| eval: false

library(tidyverse)
library(limma)
library(edgeR)
library(DESeq2)
library(ggiraph)
library(plotly)
library(gplots)
library(goseq)

```