---
title: "RNA-seq workshop setup on training environment"
format: html
date-modified: last-modified
---



### RNA-seq workshop (NZ dataset)

GitHub {{< fa brands github >}}: [https://github.com/GenomicsAotearoa/RNA-seq-data-analysis-workflow-NZ](https://github.com/GenomicsAotearoa/RNA-seq-data-analysis-workflow-NZ)

**General description:** This workshop uses shell tools in the first half and R/RStudio in the second half. It uses a couple of example datasets, which needs to be pre-loaded on the REANNZ training environment in `RNA_seq` dir. To run this workshop in a training environment, the RStudio app can be used for the entire workshop, with the terminal functionality used for the shell commands, and then R scripts will be created and run as normal in RStudio for the second half of the workshop (which is all in R from "Exploratory analysis" onwards). 

#### **Shell modules**

This workshop has been tested to work with the following modules on the REANNZ HPC:

```bash
FastQC/0.12.1
MultiQC/1.24.1-foss-2023a-Python-3.11.6
Trimmomatic/0.39-Java-1.8.0_144
STAR/2.7.10b-GCC-11.3.0-alpha
```

The Trimmomatic section requires the adapter files to be available too, which are currently at this path on the REANNZ HPC:

```bash
ADAPTERSDIR="/opt/nesi/CS400_centos7_bdw/Trimmomatic/0.39-Java-1.8.0_144/adapters" 
``` 

Learners also will need to be able to open the HTML files generated by FastQC and MultiQC. This may require javascript to be enabled in the browser.

#### **R Packages/libraries**

This workshop has been tested to work on the REANNZ HPC using:

- **RStudio-Server Version:** RStudio-Server/2024.12.1-563  
- **R Version:** R-bundle-Bioconductor/3.17-gimkl-2022a-R-4.3.1.   

The interactive plotting library is not currently loaded in this server and failed self-install (`ggiraph`)

The following R packages are required:

```{r}
#| eval: false

install.packages("tidyverse")
install.packages("ggiraph")
install.packages("BiocManager")
BiocManager::install("limma")
BiocManager::install("edgeR")
BiocManager::install("DESeq2")
BiocManager::install("gplots")
BiocManager::install("goseq")


```

Load in the required libraries:
```{r}
#| eval: false

library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(forcats)
library(tibble)
library(limma)
library(edgeR)
library(ggiraph)
library(DESeq2)
library(gplots)
library(goseq)



```

#### Datasets

- The files needed are in a directory in GitHub here: To be added... []()



\ 
